---
title: "Week 10 Day 1 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(broom)
library(janitor)
library(ggfortify)
```


```{r}
project <- clean_names(read_csv("data/project_management.csv"))
```

```{r}
project %>% 
  ggplot()+
  aes(x = estimated_length,
      y = actual_length) +
  geom_point()

```

```{r}
project %>% 
  summarise(r = cor(x = estimated_length, y = actual_length))
```

r = 0.805. This indicates a very strong positive linear correlation


```{r}
model <- lm(formula = actual_length ~ estimated_length,
            data = project)

model
```

```{r}
glance(model)
```

The estimated length coefficient says that for every day the estimated length
of the project increases by, the actual length increases by 1.223 days

R^2 of 0.647 means we can explain 64.7% of the variation in actual length using
estimated length as a predictor.


```{r}
tidy(model)
```

The p-value of estimated length is < 0.001, therefore we can say a change in 
estimated length is statistically significant in regards to a change in actual
length.

```{r}
autoplot(model)
```

The qq plot suggests a normal distribution of the data. However, the 
scale-location plot, and the residual vs fitted plot suggest a lack independence,
and a lack of heteroscedasticity.







