---
title: "w10 d3 homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(ggfortify)
library(GGally)
```



```{r}

kc_housing <- read_csv("data/kc_house_data.csv")

head(kc_housing)

kc_trimmed <- kc_housing %>% 
  select(-id,
         -date,
         -sqft_living15,
         -sqft_lot15,
         -lat,
         -long) %>%
    rename("renovated" = yr_renovated,
           "basement" = sqft_basement) %>% 
  mutate(zipcode = as.factor(zipcode),
         view = as.factor(view),
         waterfront = as.factor(waterfront),
        renovated = case_when(
           renovated == 0 ~ "0",
           TRUE ~ "1"
         ),
        renovated = as.factor(renovated),
        condition = as.factor(condition),
        basement = case_when(
          basement == 0 ~ "0",
           TRUE ~ "1"
         ),
        basement = as.factor(basement))


head(kc_trimmed)

```

```{r}
alias(price ~ .,
     kc_trimmed)
```
```{r}
ggpairs(kc_trimmed %>% 
          select(-zipcode,
                 -waterfront,
                 -view,
                 -condition,
                 -renovated,
                 -basement),
        progress = FALSE)
```

price ~ sqft_living = 0.702
          grade = 0.667
          sqft_above = 0.606
          bathrooms = 0.525
          bedrooms = 0.308


```{r}
ggpairs(kc_trimmed %>% 
          select(
                 waterfront,
                 view,
                 condition,
                 renovated,
                 basement,
                 price),
        progress = FALSE)
```


```{r}
mod1a <- lm(formula = log10(price) ~ log10(sqft_living),
           data = kc_trimmed) 

mod1b <- lm(formula = log10(price) ~ log10(sqft_above),
           data = kc_trimmed) 

mod1c <- lm(formula = log10(price) ~ grade,
           data = kc_trimmed) 
```


```{r}
autoplot(mod1a)

autoplot(mod1b)

autoplot(mod1c)
```


```{r}
summary(mod1a)

summary(mod1b)

summary(mod1c)
```


log10(price) ~ grade is best model


```{r}
kc_housing_resid <- kc_trimmed %>% 
  add_residuals(mod1c, var = "price_resid") %>% 
  select(-price, -grade)
```


```{r}
kc_housing_resid %>% 
  select(-zipcode,
         -bedrooms,
         -bathrooms,
         -sqft_living,
         -sqft_above,
         -sqft_lot,
         -floors,
         -yr_built) %>% 
  ggpairs(progress = FALSE)
```

sqft_living, bathrooms, waterfront = most interesting variables wrt price_resid


```{r}
mod2a <- lm(formula = log10(price) ~ grade + sqft_living,
            data = kc_trimmed)

mod2b <- lm(formula = log10(price) ~ grade + bathrooms,
            data = kc_trimmed)

mod2c <- lm(formula = log10(price) ~ grade + waterfront,
            data = kc_trimmed)


```


```{r}

summary(mod2a)

summary(mod2b)

summary(mod2c)

```

```{r}
autoplot(mod2a)
```


sqft_living has the highest r^2, lowest residual error, has significance,
and the diagnostic plots pass


```{r}
kc_housing_resid <- kc_trimmed %>%
  add_residuals(mod2a, "price_resid") %>% 
  select(-price, -grade, -sqft_living)
```


```{r}
kc_housing_resid %>% 
  select(-zipcode,
         price_resid,
         bedrooms,
         bathrooms,
         sqft_above,
         sqft_lot,
         yr_built,
         floors) %>% 
  ggpairs()
```

yr_built, waterfront

```{r}
mod3a <- lm(formula = log10(price) ~ grade + sqft_living + yr_built,
            data = kc_trimmed)
            
mod3b <- lm(formula = log10(price) ~ grade + sqft_living + waterfront,
            data = kc_trimmed)
```


```{r}
summary(mod3a)

summary(mod3b)
```

yr_built has a higher r^2, lower resid se, both significant

```{r}
autoplot(mod3a)
```

diagnostics pass


```{r}
kc_housing_resid <- kc_trimmed %>%
  add_residuals(mod3a, "price_resid") %>% 
  select(-price, -grade, -sqft_living, -yr_built)
```


```{r}
kc_housing_resid %>% 
  select(price_resid,
         waterfront,
         view,
         condition,
         basement,
         renovated) %>% 
  ggpairs()
```

floors, waterfront


```{r}
mod4a <- lm(formula = log10(price) ~ grade + sqft_living + yr_built + floors,
            data = kc_trimmed)

mod4b <- lm(formula = log10(price) ~ grade + sqft_living + yr_built + waterfront,
            data = kc_trimmed)
```


```{r}
summary(mod4a)

summary(mod4b)
```


Both have almost identical R^2, resid standard error, and significance

```{r}
autoplot(mod4a)

autoplot(mod4b)
```

Diagnostics plots almost the same.

waterfront has higher R^2 value


```{r}
kc_housing_resid <- kc_trimmed %>% 
  add_residuals(mod4b, var = "price_resid") %>% 
  select(-price, -yr_built, -waterfront, -grade, -sqft_living)
```




