---
title: "Week 5 Day 1 Homework"
output: html_notebook
---

```{r}
library(CodeClanData)

library(tidyverse)

library(janitor)

library(ggthemes)

colscheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```


```{r}
qb_revenue_breakdown <- clean_names(qb_revenue_breakdown)

qb_competitors <- clean_names(qb_competitors)

qb_device_data <-  clean_names(qb_device_data)

qb_monthly_sales <- clean_names(qb_monthly_sales)

qb_revenue_breakdown

```

## Take the data in the dataset qb_revenue_breakdown and make a stacked bar 
chart showing the sources of revenue across the two years in the dataset.


```{r}

ggplot(qb_revenue_breakdown) +
  geom_col(aes(x = year,
               y = revenue,
               fill = product)) +
  scale_fill_manual(values = colscheme) + 
  labs(
    y =  "Annual Revenue\n",
    x = "\nYear",
    fill = "Product"
  ) +
  theme_minimal()
  
```



## Make a line chart showing monthly sales of the “flagship product” - the 
‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but 
you will need to use filter() or subset() (base R).



```{r}
ggplot(qb_monthly_sales) +
  geom_line(data = subset(qb_monthly_sales, 
                              cashflow == "Kwikbit Unit 1 Sales"
                              ), aes(
                x = date,
                y = amount
                )
            ) +
  scale_colour_manual(values = colscheme) +
  labs(
    x = "\nDate",
    y = "Monthly Sales\n",
    title = "Monthly Sales of the KwikBit Unit 1\n"
  ) +
  theme_minimal() + 
  scale_y_continuous(limits = c(450, 650))
  
```


## Make a line chart showing monthly revenue and costs over the last year. This 
## data is also in qb_monthly_sales.


```{r}
ggplot(qb_monthly_sales) +
  geom_line(data = subset(qb_monthly_sales, 
                              cashflow != "Kwikbit Unit 1 Sales"
                              ), aes(
                x = date,
                y = amount,
                colour = cashflow
                )
            ) +
  scale_colour_manual(values = colscheme) +
  labs(
    x = "\nDate",
    y = "Total Amount\n",
    title = "Monthly Sales of the KwikBit Unit 1\n",
    fill = "Cashflow"
  ) +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 3000),
                     breaks = c(0, 1000, 1500, 2000, 2500, 3000))
  
```


## Show annual sales of personal fitness trackers over the last 5 years broken 
## down by company as a ribbon plot (use geom_area). This data is in 
## qb_competitors.



```{r}
ggplot(qb_competitors) +
  geom_area(aes(x = year,
            y = revenue,
            fill = company)) +
  scale_colour_manual(values = colscheme) +
  labs(
    y = "Revenue\n",
    x = "\nYear",
    fill = "Company",
    title = "Annual Company Revenue\n"
    ) +
  theme_minimal()

    
  
```


## Now show the sales from the four competitors as a line graph. Include an 
## extra layer that shows the data points used to make the lines.

```{r}
ggplot(qb_competitors) +
  geom_line(aes(x = year,
                y = revenue,
                colour = company
                )) +
  geom_point(aes(x = year,
                y = revenue,
                colour = company
                )) +
  scale_colour_manual(values = colscheme) +
  labs(
    x = "\nYear",
    y = "Revenue\n",
    fill = "Company",
    title = "Annual Revenue\n"
  ) +
  theme_minimal()
```


## Now the company wants to compare the number of steps that their device counts 
## vs. their competitors. Make a line graph of the number of steps throughout 
##time, and use faceting to compare between companies and people. The data for 
## this is in qb_device_data.


```{r}
qb_device_united <- qb_device_data %>% 
  mutate(mins = mins/60) %>% 
  mutate(time = hours+mins) %>% 
  select(-hours, -mins)



ggplot(qb_device_united) +
 geom_line(aes(x = time,
      y = counts,
      colour = id)) +
  facet_wrap(device ~ id) +
  scale_colour_manual(values = colscheme) +
  theme_minimal()
```

