---
title: "Hypothesis Testing & Probability"
output: html_notebook
---
```{r}
library(tidyverse)
library(infer)
library(janitor)
library(e1071)
```

1.1

Q1

```{r}
data("msleep")

head(msleep)

glimpse(msleep)

rowSums(is.na(msleep))
```


Q2

Null Hypothesis: Mean sleep total in sampled population is 7hrs

Alternative Hypothesis: Mean sleep total in sampled population is not equal to 
7hrs

CI: 5%

```{r}
observed_sleep_stat <- msleep %>% 
  summarise(
    mean_sleep = mean(sleep_total)
  )
```


```{r}

null_distribution_msleep <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 30000, type = "bootstrap") %>% 
  calculate(stat = "mean")

```

```{r}
null_distribution_msleep %>% 
  visualise(bins =30) +
  shade_pvalue(obs_stat = observed_sleep_stat,
               direction = "both")
```

```{r}
(p_value_sleep <- null_distribution_msleep %>% 
  get_pvalue(obs_stat = observed_sleep_stat,

             direction = "both"))
```

The p-value is less than 5% therefore we can reject the null hypothesis as the 
mean sleep in the sampled population does not suggest most animals sleep for 7 hrs
a night




Q3

Null Hypothesis: Mean sleep total is the same for omnivores and herbivores

Alternative Hypothesis: Mean sleep total in sampled population is significantly
different between omnivores and herbivores


CI: 5%



```{r}
msleep %>% 
  distinct(vore)
```

```{r}
msleep_vore <- msleep %>% 
  filter(vore %in% c("omni", "herbi")) 
```


```{r}
obs_vore_stat <- msleep_vore %>% 
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means",
            order = c("omni",
                      "herbi"))
```


```{r}
null_dist_vore <- msleep_vore %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesise(null = "independence") %>% 
  generate(reps = 10000, 
           type = "permute") %>% 
  calculate(stat = "diff in means",
            order = c("omni",
                      "herbi"))
```

```{r}
null_dist_vore %>% 
  visualise(bins = 30) +
  shade_pvalue(obs_stat = obs_vore_stat,
               direction = "greater")
```

```{r}
null_dist_vore %>% 
get_pvalue(obs_stat = obs_vore_stat,
           direction = "greater")

```

With a p-value of 0.12 we cant reject the null hypothesis, and so we can
say the mean sleep for omnivores and herbivores is not significantly different


Q4

Null hypothesis: The proportion of domesticated animals in the population is 5%

Alternative hypothesis: The proportion of domesticated animals in the population
is greater than 5%

CI: 5%



```{r}
msleep_domestic <- msleep %>% 
  mutate(domesticated = case_when(
    conservation == "domesticated" ~ "Yes",
    TRUE ~ "No"
  ))
```


```{r}
domestic_prop <- msleep_domestic %>% 
  summarise(prop =
    (sum(domesticated == "Yes"))/nrow(msleep_domestic)
  )
```



```{r}
null_dom_distribution <- msleep_domestic %>% 
  specify(response = domesticated,
          success = "Yes") %>% 
  hypothesise(null = "point",
              p = 0.05) %>% 
  generate(reps = 30000,
           type = "draw") %>% 
  calculate(stat = "prop")
```



```{r}
null_dom_distribution %>% 
  visualise() +
  shade_pvalue(obs_stat = domestic_prop,
               direction = "greater")
```

```{r}
null_dom_distribution %>% 
  get_p_value(obs_stat = domestic_prop,
              direction = "greater")
```
With a p-value of 0.008 and a CI of 5% we can reject the null hypothesis that
5% of the animals are domesticated, and can say that significantly more than 5% 
of animals in the sample are domesticated.


1.2

Q1

Null hypothesis: proportion of towns population who know about the coffee shop 
is 0.4

Alternative hypothesis: The proportion of people who know about the coffee shop 
is more than 0.4

We would use a draw method to generate the null distributiom



Q2

Null hypothesis: The position of the banner has no effect on click-through rate,
and the click through rate is the same for both groups

Alternative hypothesis: One of the banner positions has a higgher CTR than the 
other

Use the draw method to generate the null distribution



Q3

Null hypothesis: The parts all meet the dimensions criteria

Alternative hypothesis: The parts do not all meet the dimensions criteria and have
drifted

Use bootstrapping to generate the null distribution


1.3

Q1

The p-value is greater than the CI of 5%. This suggests that the proportion from
the sample would be 7% likely to fall in the null-distribution. Therefore
we can't reject the null hypothesis.


Q2

The CI is greater than the p-value so we have to reject the null hypothesis as
one of the banner shas a higher CTR than the other

Q3

p-value is considerable higher than the CI. Therefore the parts dimensions have 
drifted significantly and we must go with the alternaive hypothesis:







