---
title: "Week 6 Day 1 Homework"
output: html_notebook
---

```{r}
library(gtools)
library(janitor)
library(tidyverse)

titanic <- read_csv("data/titanic.csv")

head(titanic)

titanic %>% 
  distinct(class)
```

```{r}
titanic_crew <- 
  titanic %>% 
  mutate(crew = case_when(
    str_detect(class, "^[0-9]+")  ~ 0,
   TRUE ~ 1
  )) %>% 
  select(survived, crew)
```

```{r}
prob_table <- titanic_crew %>% 
  tabyl(crew, survived) %>% 
   adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all")

prob_table
  
```

prob(survived | crew) = prob(crew & survived) / prob(crew)

= 0.09560489 / 0.4032623
```{r}

0.09560489 / 0.4032623

```

= 0.237




prob(survived | passenger) = prob(passenger & survived) / prob(passenger)

= 0.22655188 / 0.5967377

```{r}

0.22655188 / 0.5967377

```

= 0.37956507




1.2

Q1: 1, 2, 3, 4 = 4 different rolls less than 5

4/6 = 2/3 = 0.67


Q2: 
```{r}
permutations(6, 3, repeats.allowed = TRUE) %>% 
  nrow()
```

216


Q3:

```{r}
dice_rolls_3 <- as.tibble(permutations(6, 3, repeats.allowed = TRUE)) %>% 
  mutate(total = V1 + V2 + V3)
```


```{r}
dice_rolls_3 %>% 
  filter(total == 5 | total == 6 | total == 7) %>% 
  nrow()
```
31 different outcomes where the total = 5, 6, or 7



```{r}
31/216
```

0.1435 is the probability of the above event occurring





Q4:

```{r}

1/5 * 1/4 * 1/3 * 1/2

```

OR

```{r}
1/factorial(5)
```


0.00833333


Q5:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the 
dice, left to right?

```{r}
(1/6)^6
```

2.15e-5


what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the 
dice regardless of order?

```{r}
(6/6) * (5/6) * (4/6) * (3/6) * (2/6) * (1/6)
```

0.0154 



Q6:

1/2


