---
title: "Week 6 Day 3 Homework"
output: html_notebook
---

```{r}
library(janitor)
library(tidyverse)
library(e1071)
library(infer)
```

Q1 

```{r}
ames <- clean_names(read_csv("data/ames.csv"))
```

```{r}
glimpse(ames)

head(ames)
```


Q2

```{r}
ames %>% 
  ggplot() +
  aes(x = lot_area) +
  geom_histogram(binwidth = 5000)
```

```{r}
ames %>% 
  summarise(
    skewness = skewness(lot_area)
  )
```
```{r}
ames %>% 
  filter(lot_area <= 25000) %>% 
  summarise(skewness = skewness(lot_area))
```

The data is positively skewed very heavily, with a skewness of 12.8. Up to about
25000 the data is distributed fairly normally with a skewness of 0.54


Q3

```{r}

infer_area <- ames %>%
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")

infer_area

```

```{r}
infer_area %>% 
  visualise(bins = 30)
  
```


Q4


```{r}
ci_95 <- infer_area %>% 
  get_ci(level = 0.95,
         type = "percentile")
```


```{r}
infer_area %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_95)
```


Q5

```{r}
ci_99 <- infer_area %>% 
  get_ci(level = 0.99,
         type = "percentile")
```


```{r}
infer_area %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = ci_99)
```

The shaded area is wider. This is expected as to be 99% confident on the area a 
random mean of lot area would fall in we need to cover a larger number of potential
values.


Q6

```{r}
mean_lot_area <- infer_area %>% 
  summarise(
    mean_area = mean(stat)
  )

mean_lot_area
```

The point estimate of the lot area in the sampled data is 10146.5 units^2



Extension


```{r}
ames_1920 <- ames %>%
  select(year_built) %>% 
 mutate(pre_1920 = case_when(
   year_built < 1920 ~ "Yes",
   TRUE ~ "No"
 ))
  
```

```{r}
bootstrap_1920 <- ames_1920 %>% 
  specify(response = pre_1920, success = "Yes") %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r}
ci_1920_95 <- bootstrap_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
```

```{r}
bootstrap_1920 %>% 
  visualise() +
  shade_ci(endpoints = ci_1920_95)
```

```{r}
mean_1920_prop <- bootstrap_1920 %>% 
  summarise(
    mean = mean(stat)
  )
```






```{r}
bootstrap_1920_2 <- ames_1920 %>% 
  specify(response = pre_1920, success = "Yes") %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "prop")
```

```{r}
ci_1920_95_2 <- bootstrap_1920 %>% 
  get_ci(level = 0.95, type = "percentile")
```

```{r}
bootstrap_1920_2 %>% 
  visualise() +
  shade_ci(endpoints = ci_1920_95)
```

```{r}
mean_1920_prop_2 <- bootstrap_1920_2 %>% 
  summarise(
    mean = mean(stat)
  )
```



